Adaptive Sequential Model Selection

### 2015-05-07 paper.tex
just commented out the figures
added figures for paper, uncommented figures

To obtain a sequence of $p$-values, we must specify what model selection algorithm $M_{[d]}$ to use, as well as how to construct $p$-values at each step. In this section we consider what conditions are sufficient to guarantee that the resulting $p$-value sequence is independent. Sections~\ref{sec:pvalSP}--\ref{sec:modelSPSP} discuss sufficient conditions on the $p$-values and the selection algorithm under which single-step $p$-values are automatically independent. Section~\ref{sec:selectionVariables} discusses how we can create independent $p$-values by conditioning on finer selection variables at each step.

Essentially, we will want to partition the information in $Y$ according to the filtration:
\begin{align}\nonumber
  \sF(M_0,T_0) &\underlabel_{\text{selection } 1} 
  \sF(M_{[1]},T_0) \underlabel_{\text{inference } 1}
  \sF(M_{[1]},T_1) \quad \sub \;\;\cdots\\[8pt]
  \label{eq:infoPartition}
  \cdots\;\; \sub \quad&
  \sF(M_{[d-1]},T_{d-1}) \underlabel_{\text{selection } d}
  \sF(M_{[d]},T_{d-1}) 
  \underlabel_{\text{inference } d}
  \sF(M_{[d]}, T_d)
\end{align}

\subsubsection{Generalized Selected-Model $p$-Values}\label{sec:pvalSP}

For a candidate pair $(m_{k-1},m_k)$ of models to test at step $k$, define the selection event $A = \{M_{k-1},M_k\}$. We say $p(Y)$ is a {\em generalized selected-model $p$-value} for testing $m_{k-1}$ against $m_k$ at step $k$ if it is ``based on'' the law
\[
\L_{m_{k-1}}\left(T_k \;\;\mid\;\; T_{k-1},\; M_{k-1}=m_{k-1},\;M_k=m_k\right)
\]
for some minimal sufficient statistics $T_{k-1}(Y)$ and $T_k(Y)$ of $m_{k-1}$ and $m_k$, respectively. More precisely, $p(Y)$ must be uniform or conservative conditional on $T_{k-1}(Y)$, and it must be a function of $T_k(Y)$ on $A$.

>>>>

To obtain a sequence of $p$-values, we must specify what model selection algorithm $M_{[d]}$ to use, as well as how to construct $p$-values at each step. In this section we consider what conditions are sufficient to guarantee that the resulting $p$-value sequence is independent.

\begin{comment}
Sections~\ref{sec:pvalSP}--\ref{sec:modelSPSP} discuss sufficient conditions on the $p$-values and the selection algorithm under which single-step $p$-values are automatically independent. Section~\ref{sec:selectionVariables} discusses how we can create independent $p$-values by conditioning on finer selection variables at each step.

Essentially, we will want to partition the information in $Y$ according to the filtration:
\begin{align}\nonumber
  \sF(M_0,T_0) &\underlabel_{\text{selection } 1} 
  \sF(M_{[1]},T_0) \underlabel_{\text{inference } 1}
  \sF(M_{[1]},T_1) \quad \sub \;\;\cdots\\[8pt]
  \label{eq:infoPartition}
  \cdots\;\; \sub \quad&
  \sF(M_{[d-1]},T_{d-1}) \underlabel_{\text{selection } d}
  \sF(M_{[d]},T_{d-1}) 
  \underlabel_{\text{inference } d}
  \sF(M_{[d]}, T_d)
\end{align}
\end{comment}

\subsubsection{Independent $p$-Values and the Sufficiency Principle}\label{sec:pvalSP}

Assume that every candidate model $m$ has a set of minimal sufficient statistics $T(y; \;m)$. For linear regression, the sufficient statistics for $M(E)$ are $X_E'Y$ if $\sigma^2$ is known and  $(X_E'Y,\|Y\|)$ otherwise. At step $k$, let $T_k(Y) = T(Y; \;M_k(Y))$ denote the sufficient statistics for the model actually chosen --- for example, $X_{E_k(Y)}'Y$.

For a candidate pair $(m_{k-1},m_k)$ of models to test at step $k$, define the selection event $A = \{M_{k-1} = m_{k-1}, M_k=m_k\}$. The $p$-value for this pair, $p_{k,m_{k-1},m_k}$ satisfies the sufficiency principle if 
\[
\P_F\left(p_{k,m_{k-1},m_k}(Y) \mid M_{k-1}=m_{k-1}, M_k=m_k\right)
\]
This is what we mean when we say $p_{k,m_{k-1},m}$ is ``based on'' the law
\[
\L_{m_{k-1}}\left(T_k \;\;\mid\;\; T_{k-1},\; M_{k-1}=m_{k-1},\;M_k=m_k\right)
\]
for some minimal sufficient statistics $T_{k-1}(Y)$ and $T_k(Y)$ of $m_{k-1}$ and $m_k$, respectively. More precisely, $p(Y)$ must be uniform or conservative conditional on $T_{k-1}(Y)$, and it must be a function of $T_k(Y)$ on $A$.
